---
title: "Blood branded bandage anaylses"
output:
  pdf_document:
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---
# Packages and reading data
```{r}
# Packages
library(tidyverse) # general use
library(afex) # running ANOVA
library(emmeans) # follow up effects on ANOVA
library(ggsignif) # 
library(ggtext) # adding color in title

# Read and clean data
data<- read_csv("data.csv")%>%
  filter(attention.check == "pass")%>% # only including participants who passed
  rowid_to_column(var = "id")%>% # assign id to rows
  mutate(across(where(is.character),factor)) # convert all characters to factor
```

# Creating measures
```{r}
data<-data%>%
  mutate(
    generous = round(select(.,selfish,insincere,impure,bad,mean,
                            altruistic,sincere,pure,good,nice)%>%rowMeans(),2),
    warmth = round(select(.,warm, sociable, happy, agreeable, 
                          enthusiastic, easy.going, playful, funny)%>%rowMeans(),2),
    morality = round(select(.,courageous, fair, principled, responsible,
                            just, honest,trustworthy, loyal)%>%rowMeans(),2),
    competence = round(select(.,skillful,competent,talented,effective,capable,intelligent)
                       %>%rowMeans(),2),
    health = round(select(.,fit, healthy, disease)
                       %>%rowMeans(),2),
    attractive = round(select(.,attr,classy,beauty,elegant,sexy)%>%rowMeans(),2),
    self.promotion = round(select(.,show.off,impress,complimented,attention,special)
                           %>%rowMeans(),2)
    )
```

# Confirmatory analyses
For each dependent variable we run an ANOVA with the two main effects (condition and participant gender) and the interaction term of the main effects.
The Holm-Bonferroni correction was used to adjust the alpha level for the ANOVAs to control for inflated Type 1 error arising from conducting exploratory analyses. Traits (6 measures) and benefits (3 measures) are separate hypotheses. Thus the corrected alpha level for ANOVA with the lowest p value testing each of the hypothesis is:
- Traits = 008 (.05/6)
- Benefits = .017 (.05/3)
The next lowest p-value would be tested against tested against (.05/5) .01 in traits and (.05/2) .025 in benefits, and so on. 
## Generosity
```{r}
# ANOVA Model
generous.model <-aov_car(generous~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
# Follow main effect of condition
emmeans(generous.model,~condition)%>%pairs(., adjust = "tukey")
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(generous),
                                       sd = sd(generous),
                                       n = n())
# Follow up main effect of gender
emmeans(generous.model,~gender)%>%pairs(.,adjust = "tukey")
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(generous),
                                       sd = sd(generous),
                                       n = n())

# Follow interaction
emmeans(generous.model,~condition|gender)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(gender,condition)%>%summarise(mean = mean(generous),
                                              sd = sd(generous))
```

## Morality
```{r}
# ANOVA Model
morality.model<- aov_car(morality~condition*gender+ Error (id),
                        data = data, 
                        anova_table = list (es = "pes"))

# Follow up main effect of condition
emmeans(morality.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(morality),
                                       sd = sd(morality))

# Follow up main effect of gender
emmeans(morality.model,~gender)%>%pairs(., adjust = "tukey") # gender
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(morality),
                                    sd = sd(morality))
```

## Warmth
```{r}
# ANOVA Model
warmth.model<- aov_car(warmth~condition*gender+ Error (id),
                      data = data, 
                      anova_table = list (es = "pes"))
# Follow up main effect of condition
emmeans(warmth.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(warmth),
                                       sd = sd(warmth))
# Follow up main effect of gender
emmeans(warmth.model,~gender)%>%pairs(., adjust = "tukey")
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(warmth),
                                    sd = sd(warmth))
```

## Competence
```{r}
# ANOVA Model
competence.model<- aov_car(competence~condition*gender+ Error (id),
                          data = data, 
                          anova_table = list (es = "pes"))
# Follow up main effect of condition
emmeans(competence.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(competence),
                                       sd = sd(competence))

# Follow up main effect of gender
emmeans(competence.model,~gender)%>%pairs(., adjust = "tukey") # gender
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(competence),
                                       sd = sd(competence))
```
## Health
```{r}
# ANOVA Model
health.model<- aov_car(health~condition*gender+ Error (id),
                      data = data, 
                      anova_table = list (es = "pes"))

# Follow up main effect of condition
emmeans(health.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(health),
                                       sd = sd(health))
```

## Self-promotion
```{r}
# ANOVA Model
promotion.model<- aov_car(self.promotion~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
```

## Attractiveness
```{r}
# ANOVA Model
attractive.model<- aov_car(attractive~condition*gender+ Error (id),
                          data = data, 
                          anova_table = list (es = "pes"))
```

## Long-term desirability
```{r}
# ANOVA Model
long.att.model<- aov_car(long.att~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
```

## Short-term desirability
```{r}
# ANOVA Model
short.att.model<- aov_car(short.att~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
```


## Visualisation
Plots the key results of generosity, health, and self promotion
```{r}
plot<-data%>%
  mutate(condition = fct_recode(condition,
                                "Blood bandage" = "blood",
                                "Plain bandage" = "bandage",
                                "No bandage" = "control"
                                ))%>%
  select(id,condition,self.promotion,health,generous) %>% # Select columns of interest
  # Make longer to plot with facet
  pivot_longer(cols = -c(id,condition),
               names_to = "trait",
               values_to = "rating") %>% 
  ggplot(aes(x = condition, y = rating, color = condition)) +
  geom_boxplot() +
  #ggsignif::geom_signif(comparisons = list(c("Blood bandage","Plain bandage","No bandage")),map_signif_level = T) +
  geom_jitter(alpha = 0.2,show.legend = F) +
  stat_summary(fun =mean,geom="point", show.legend = F,
                           shape=18, size=5) +
  ggrepel::geom_label_repel(stat = 'summary', fun=mean, 
                            aes(label = str_c("Mean = ",round(..y.., 2))), nudge_x = 0.15, 
                            show.legend = F,box.padding = 3, size = 4,
                            segment.angle = 20,arrow = arrow(length = unit(0.015, "npc"))) +
  facet_wrap(~recode_factor(trait,
                            generous = "Generosity",
                            health = "Healthiness",
                            self.promotion = "Self promotional"),
                     nrow = 1) +
  scale_y_continuous(breaks = seq(1, 7, by = 1)) +
  scale_color_manual(values = c("#414487","#23888e","#35b779")) + # Choose colors
  labs(title = "How do people judge <span style = 'color:#23888e;'>branded bandage</span>,<span style = 'color:#414487;'>plain bandage</span>, and <span style = 'color:#35b779;'>no bandage</span> wearers?",
       subtitle = "Wearing a <span style = 'color:#23888e;'>branded bandage</span> was rated as more generous, equally healthy and not self-promotional than wearing <span style = 'color:#35b779;'>no bandage</span>. <br>Compared to wearing <span style = 'color:#35b779;'>no bandage</span>, having a <span style = 'color:#414487;'>plain bandage</span>was also seen as more generous but also less healthier.",
       x = NULL, y = "Level") +
  theme_light() +
  theme(
      # keeps only horizontal lines
      panel.grid.major.x= element_blank(), 
      panel.grid.minor.x = element_blank(),
      # Title & subtitle
      plot.title = element_markdown(size = 25, hjust = 0, vjust = 0.5, face = "bold",
                                margin = margin(b = .3, unit = "cm")),
      plot.subtitle = element_markdown(size = 15, hjust = 0, vjust = 0.5, colour = "grey45",
                                   margin = margin(b = 0.3, unit = "cm")),
      # Caption
      plot.caption = element_text(size = 10, hjust = 1, face = "italic", colour = "grey70",
                                  margin = margin(t = 0.1, unit = "cm")),
      # X - axis
      axis.title.x = element_text(margin = margin(t = .5,unit = "cm"), size = 13,color = "grey50"),
      axis.text.x = element_blank(),
      axis.text.y = element_text(size = 13),
      axis.ticks.x = element_blank(),
      # Y - axis
      axis.title.y = element_text(margin = margin(r = .5, unit = "cm"), size = 13, color = "grey50",angle = 90),
      # Legend
      legend.position = "none",
      # Facet wrap
      strip.background = element_rect(fill = "white"),
      strip.text = element_text(size = 12,face = "bold",color = "black"),
    )

# Save
ggsave(plot,filename = "results.png",width = 14,height = 6,dpi = 600)

```


