---
title: "Blood branded bandage anaylses"
output:
  pdf_document:
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---
# Packages and reading data
```{r}
# Packages
library(tidyverse) # general use
library(afex) # running ANOVA
library(emmeans) # follow up effects on ANOVA

# Read and clean data
data<- read_csv("data.csv")%>%
  filter(attention.check == "pass")%>% # only including participants who passed
  rowid_to_column(var = "id")%>% # assign id to rows
  mutate_if(is.character, as.factor) # convert all characters to factor
```

# Creating measures
```{r}
data<-data%>%
  mutate(
    generous = round(select(.,selfish,insincere,impure,bad,mean,
                            altruistic,sincere,pure,good,nice)%>%rowMeans(),2),
    warmth = round(select(.,warm, sociable, happy, agreeable, 
                          enthusiastic, easy.going, playful, funny)%>%rowMeans(),2),
    morality = round(select(.,courageous, fair, principled, responsible,
                            just, honest,trustworthy, loyal)%>%rowMeans(),2),
    competence = round(select(.,skillful,competent,talented,effective,capable,intelligent)
                       %>%rowMeans(),2),
    health = round(select(.,fit, healthy, disease)
                       %>%rowMeans(),2),
    attractive = round(select(.,attr,classy,beauty,elegant,sexy)%>%rowMeans(),2),
    self.promotion = round(select(.,show.off,impress,complimented,attention,special)
                           %>%rowMeans(),2)
    )
```

# Confirmatory analyses: ANOVAs
For each dependent variable we run an ANOVA with the two main effects (condition and participant gender) and the interaction term of the main effects.
The Holm-Bonferroni correction was used to adjust the alpha level for the ANOVAs to control for inflated Type 1 error arising from conducting exploratory analyses. Traits (6 measures) and benefits (3 measures) are separate hypotheses. Thus the corrected alpha level for ANOVA with the lowest p value testing each of the hypothesis is:
- Traits = 008 (.05/6)
- Benefits = .017 (.05/3)
The next lowest p-value would be tested against tested against (.05/5) .01 in traits and (.05/2) .025 in benefits, and so on. 
## Generosity
```{r}
# ANOVA Model
generous.model <-aov_car(generous~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
# Follow main effect of condition
emmeans(generous.model,~condition)%>%pairs(., adjust = "tukey")
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(generous),
                                       sd = sd(generous),
                                       n = n())
# Follow up main effect of gender
emmeans(generous.model,~gender)%>%pairs(.,adjust = "tukey")
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(generous),
                                       sd = sd(generous),
                                       n = n())

# Follow interaction
emmeans(generous.model,~condition|gender)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(gender,condition)%>%summarise(mean = mean(generous),
                                              sd = sd(generous))
```

## Morality
```{r}
# ANOVA Model
morality.model<- aov_car(morality~condition*gender+ Error (id),
                        data = data, 
                        anova_table = list (es = "pes"))

# Follow up main effect of condition
emmeans(morality.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(morality),
                                       sd = sd(morality))

# Follow up main effect of gender
emmeans(morality.model,~gender)%>%pairs(., adjust = "tukey") # gender
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(morality),
                                    sd = sd(morality))
```

## Warmth
```{r}
# ANOVA Model
warmth.model<- aov_car(warmth~condition*gender+ Error (id),
                      data = data, 
                      anova_table = list (es = "pes"))
# Follow up main effect of condition
emmeans(warmth.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(warmth),
                                       sd = sd(warmth))
# Follow up main effect of gender
emmeans(warmth.model,~gender)%>%pairs(., adjust = "tukey")
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(warmth),
                                    sd = sd(warmth))
```

## Competence
```{r}
# ANOVA Model
competence.model<- aov_car(competence~condition*gender+ Error (id),
                          data = data, 
                          anova_table = list (es = "pes"))
# Follow up main effect of condition
emmeans(competence.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(competence),
                                       sd = sd(competence))

# Follow up main effect of gender
emmeans(competence.model,~gender)%>%pairs(., adjust = "tukey") # gender
# Descriptives
data%>%group_by(gender)%>%summarise(mean = mean(competence),
                                       sd = sd(competence))
```
## Health
```{r}
# ANOVA Model
health.model<- aov_car(health~condition*gender+ Error (id),
                      data = data, 
                      anova_table = list (es = "pes"))

# Follow up main effect of condition
emmeans(health.model,~condition)%>%pairs(.,adjust = 'tukey')
# Descriptives
data%>%group_by(condition)%>%summarise(mean = mean(health),
                                       sd = sd(health))
```

## Self-promotion
```{r}
# ANOVA Model
promotion.model<- aov_car(self.promotion~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
```

## Attractiveness
```{r}
# ANOVA Model
attractive.model<- aov_car(attractive~condition*gender+ Error (id),
                          data = data, 
                          anova_table = list (es = "pes"))
```

## Long-term desirability
```{r}
# ANOVA Model
long.att.model<- aov_car(long.att~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
```

## Short-term desirability
```{r}
# ANOVA Model
short.att.model<- aov_car(short.att~condition*gender+ Error (id),
                         data = data, 
                         anova_table = list (es = "pes"))
```

# Exploratory analyses
## Moderated Mediation
```{r}
# Smaller working DF
wdata<- data%>%select(condition,gender,short.att,long.att,attractive,generous) 

# DF: Blood vs Control
df1 <- wdata%>%filter(condition == 'blood'|condition == 'control')%>%droplevels() # make pairwise comparison
df1<-df1%>%mutate(gender = ifelse(gender == 'Male',0,1)) # convert gender 
df1<- make_numeric(var = 'condition', ref = 'control', newvar = 'condition1',data = df1) # turn condition to numeric

# DF: Bandage vs Control
df2 <- wdata%>%filter(condition == 'bandage'|condition == 'control')%>%droplevels() # make pairwise comparison
df2<- make_numeric(var = 'condition', ref = 'control', newvar = 'condition1',data = df2) # condition to numeric
df2<-df2%>%mutate(gender = ifelse(gender == 'Male',0,1)) # convert gender 

# DF: Bandage vs Blood
df3 <- wdata%>%filter(condition == 'blood'|condition == 'bandage')%>%droplevels() # make pairwise comparison
df3<- make_numeric(var = 'condition', ref = 'bandage', newvar = 'condition1',data = df3) # condition to numeric
df3<-df3%>%mutate(gender = ifelse(gender == 'Male',0,1)) # convert gender 
```
### Blood vs control
```{r}
# Long term desirability
mod7.long <- model7(iv = 'condition1',
               dv = 'long.att',
               med = 'generous',
               mod = 'gender',
               data = df1)

# Short term desirability
mod7.short <- model7(iv = 'condition1',
                          dv = 'short.att',
                          med = 'generous',
                          mod = 'gender',
                          data = df1)

# Attractiveness
mod7.attractive <- model7(iv = 'condition1',
                          dv = 'attractive',
                          med = 'generous',
                          mod = 'gender',
                          data = df1)

# Print models
print(mod7.long)
print(mod7.attractive)
print(mod7.short)

```

### Bandage vs control
```{r}
# Long term
mod7.v2.long <- model7(iv = 'condition1',
                          dv = 'long.att',
                          med = 'generous',
                          mod = 'gender',
                          data = df2)

# Short term
mod7.v2.short <- model7(iv = 'condition1',
                           dv = 'short.att',
                           med = 'generous',
                           mod = 'gender',
                           data = df2)

# Attractiveness
mod7.v2.attractive <- model7(iv = 'condition1',
                                dv = 'attractive',
                                med = 'generous',
                                mod = 'gender',
                                data = df2)

# Print models
print(mod7.v2.long)
print(mod7.v2.short)
print(mod7.v2.attractive)
```

### Bandage vs blood
```{r}
# Long term
mod7.v3.long <- model7(iv = 'condition1',
                          dv = 'long.att',
                          med = 'generous',
                          mod = 'gender',
                          data = df3)
      
# Short term
mod7.v3.short <- model7(iv = 'condition1',
                           dv = 'short.att',
                           med = 'generous',
                           mod = 'gender',
                           data = df3)
      
# Attractiveness
mod7.v3.attractive <- model7(iv = 'condition1',
                                dv = 'attractive',
                                med = 'generous',
                                mod = 'gender',
                                data = df3)
      

# Print models
print(mod7.v3.long)
print(mod7.v3.short)
print(mod7.v3.attractive)
```


## Reviewer requested analyses: Three way anova with blood status,bandage condition, and participant gender
```{r}
# Generous
summary(aov_car(generous~condition*blood*gender+ Error (id),
                         data = data, anova_table = list (es = "pes")))
# Competence
summary(aov_car(competence~condition*blood*gender+ Error (id),
                          data = data,anova_table = list (es = "pes")))
# Morality
summary(aov_car(morality~condition*blood*gender+ Error (id),
                        data = data, anova_table = list (es = "pes")))
# Warmth
summary(aov_car(warmth~condition*blood*gender+ Error (id),
                      data = data, anova_table = list (es = "pes")))
# Health
summary(aov_car(health~condition*blood*gender+ Error (id),
                      data = data, anova_table = list (es = "pes")))

# Self promotion
summary(aov_car(self.promotion~condition*blood*gender+ Error (id),
                         data = data,anova_table = list (es = "pes")))
# Attractive
summary(aov_car(attractive~condition*blood*gender+ Error (id),
                          data = data,anova_table = list (es = "pes")))

# Long term attractiveness
summary(aov_car(long.att~condition*blood*gender+ Error (id),
                         data = data,anova_table = list (es = "pes")))
# Short term attractiveness
ea_model<-aov_car(short.att~condition*blood*gender+ Error (id),
                         data = data,anova_table = list (es = "pes"))
## Follow up two way interaction in short-term attractiveness
emmeans(ea_model,~gender|blood)%>%pairs(.,adjust = "tukey")
## Descriptives
data%>%group_by(blood,gender)%>%summarise(m = mean(short.att), sd = sd(short.att))

```

## Plotting interaction
```{r}
# OLD 
data%>%
  mutate(condition = fct_recode(condition,
                                "Blood branded bandage" = "blood",
                                "Plain bandage" = "bandage",
                                "Control (No bandage)" = "control"
                                ))%>%
  ggplot(aes(x = condition, y = generous, color = condition)) +
  geom_boxplot(show.legend = F) +
  geom_jitter(alpha = 0.2,show.legend = F) +
  stat_summary(fun =mean,geom="point", show.legend = F,
                           shape=18, size=5) +
  #stat_n_text(text.box = T) +
  ggrepel::geom_label_repel(stat = 'summary', fun=mean, aes(label = round(..y.., 2)), nudge_x = 0.1, hjust = 0,show.legend = F) +
  facet_wrap(~gender, nrow = 1) +
  scale_y_continuous(limits = c(0,8), breaks = seq(1, 7, by = 1)) +
  labs(x = "Bandage type", y = "Perception of generosity") +
  scale_color_viridis_d() +
  theme_bw() +
  ggsave("/Users/michaellam/Desktop/R_DATA_FILES/bandage revisions/toupload/s1_plot.png", units = "in",  height = 6, width = 12)

```


